MTSN: Multi-Task Temporal and Spatial Network for High-Precision Event Spotting in Volleyball Videos

### 2024-10-16 Paper.tex
update

\title{[Draft Title] Spatial Temporal Event Spotting in Volleyball Videos}

@@

\keywords{Temporally Precise Spotting, Video Understanding, Spatial Temporal Event Spotting, Volleyball, Sport, Deep Learning}

\abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}

>>>>

% \title{Multi-task Architecture for Temporally and Spatially Precise Event Spotting in Volleyball Videos}
% \title{Dual-Objective Deep Learning Architecture for Accurate Temporal and Spatial Event Detection in Volleyball}
\title{MTSN: Multi-Task Temporal and Spatial Network for High-Precision Event Spotting in Volleyball Videos}
% \title{Multi-Task Temporal-Spatial Deep Learning for Accurate Event Localization in Volleyball Videos}
% \title{Multi-Task Deep Framework for Accurate Temporal and Spatial Event Detection in Volleyball Videos}

@@

\keywords{Precise Event Spotting, Sports Video Understanding, Spatial Temporal Event Spotting, Deep Learning, Volleyball}

% \abstract{The abstract should summarize the contents of the paper and should contain at least 70 and at most 200 words. The text must be set to 9-point font size.}
\abstract{Precise event spotting is crucial in applications like sports analysis, where both temporal and spatial accuracy are key, especially in fast-paced sports like volleyball. We introduce a new task: high-precision spatial-temporal event spotting in volleyball videos, requiring detection of both when and where events occur. To address this, we develop a novel volleyball dataset annotated for temporal and spatial event localization and propose a multi-task deep learning model that jointly predicts event timing and spatial coordinates. Adding spatial prediction improves temporal event detection by ???\%, demonstrating the synergy between these tasks. To the best of our knowledge, this is the first work tackling this task, establishing a strong baseline and providing a foundation for future research in spatial-temporal event spotting.}
